%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Network Engineer} % Job title
    {Crown Castle Inc.} % Organization
    {Herndon, VA} % Location
    {Apr. 2023 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Provide support to network expansion initiatives and network troubleshooting.}
        \item {Migrate legacy automation scripts to Ansible / Juniper Snapshot Administrator as needed.}
        \item {Migrate legacy CRON jobs to Jenkins to easier access and management by the engineering team.}
        \item {Created a standard library of configuration templates that can be used with Ansible and stand alone scripts.}
        \item {Educate team members on the use of automation tools as developed.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Network Engineer} % Job title
    {FirstLight Fiber} % Organization
    {Albany, NY} % Location
    {Nov. 2021 - Apr. 2023} % Date(s)
    {
      \begin{cvitems}
        \item {Provide SME level consultation for internal groups across all networking disciplines; cloud, enterprise and service provider.}
        \item {Develop engineering work packages detailing all network hardware installation requirements.}
        \item {Collaborate with boundary partners to install and connect new network hardware.}
        \item {Commission new and replacement equipment for service.}
        \item {Optimized backbone routing using NetworkX.}
        \item {Manage route object authorizations in ARIN's RPKI service.}
        \item {Migrated IRR objects that were spread across 2 registries to ARINs IRR service. Giving the organization 1 portal to manage all IRR objects.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Network Engineer II} % Job title
    {Cox Communications LLC.} % Organization
    {Springfield, VA} % Location
    {Oct. 2014 - Nov. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Design and Provision services on a Cable Service Provider / Multiple System Operator network.}
        \item{Develop engineering work packages detailing all network hardware installation requirements.}
        \item{Collaborate with boundary partners to install and connect new network hardware.}
        \item{Commission new and replacement equipment for service.}
        \item{Participates in a national automation team and working group.}
        \item{Automate the generation of switch configurations with input validation using templates.}
        \item{Manage IP scheme, allocation and reclamation of IPv4 and IPv6 subnets.}
        \item{Provide documentation / presentations to internal customers about changes in the network directly affecting them.}
        \item{Troubleshoot issues with internal and external customers as needed.}
        \item{Maintain network asset records in Datacenter Infrastructure Management software.}
        \item{Participate in RFP development and vendor selection for new network hardware.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {DOCSIS Engineer II} % Job title
    {Cox Communications LLC.} % Organization
    {Springfield, VA} % Location
    {Apr. 2007 - Oct. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Provision business and residential style services across the Cable Modem Termination System.}
        \item {Process design for service enablement to reduce impact on customers.}
        \item {Provided Tier III support for customer issues.}
        \item {Prepared Cox Communication network for IPv6 and participated in World IPv6 Day.}
        \item {Managed the IP scheme and allocation and reclamation of IPv4 and IPv6 subnets.}
        \item {Managed 2 complete hardware upgrades of the CMTS network.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Unix Systems Administrator} % Job title
    {RealNetworks Inc.} % Organization
    {Reston, VA} % Location
    {Dec. 2006 - Apr. 2007} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Maintained parity between production and development environments.}
        \item {Packaged and deployed releases of software.}
        \item {Developed and maintained CDN verification framework for digital assets.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Technical Support Engineer} % Job title
    {WiderThan Inc.} % Organization
    {Reston, VA} % Location
    {Nov. 2004 - Dec. 2006} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Supported SS7 and Ethernet networked applications for cellular telephone companies.}
        \item {Trained and maintained relationships with customer's product support staff.}
        \item {Managed and trained team of seven support engineers.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {System Operations Center Specialist} % Job title
    {Cox Communications Inc.} % Organization
    {Springfield, VA} % Location
    {Apr. 2002 - Nov. 2004} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Triaged RF and Ethernet network issues and provided analysis to the next tier of support.}
        \item {Interfaced with customers to ensure services were restored quickly.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Customer Care Representative II} % Job title
    {Cox Communications Inc.} % Organization
    {Chantilly, VA} % Location
    {Jan. 2001 - Apr. 2002} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Provided support for high-speed internet and related services.}
        \item {Supported the county government affairs liaison group to resolve sensitive customer issues.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Combat Engineer} % Job title
    {United States Army} % Organization
    {USA} % Location
    {Jul. 1994 - Jan. 2001} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Shaped the battlefield to provide a tactical advantage to the Infantry.}
        \item {Provided route clearance operations to the Infantry.}
        \item {Provided training to team members on basic combat skills as well as MOS specific skills.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
